Composite Bayesian inference

### 2018-12-01 papers/composite_inference/draft.tex
re-birth of super composite likelihood

>>>>

\section{Super composite likelihood}
\label{sec:super}

When chosen for computational simplicity, clues may not only convey limited information at individual level: their informativeness may also be very much hypothesis-dependent. Consider, for instance, diagnosing a disease from a routine medical checkup. Body temperature may point to a bacterial infection by comparison with normality, but would not help detecting a non-infectious cardiovascular disease -- and conversely for, say, blood pressure.

This motivates a more general setting where clues can be weighted differently depending on hypotheses.

What happens if we use mean-values constraints conditional on $x$ instead of jointly averaged over $x$ and $y$? This boils down to picking functions of the form:
$$
\chi(x-a)\ell_i(x,y)
$$

The answer is that the maxent solution has the form:
$$
p_\lambda(x|y) = \pi(x) \prod_i p(z_i|x)^{\lambda_i(x)}
$$

In other words, the weights become dependent on the variable of interest. This is the super composite likelihood idea.
